\vspace{\baselineskip} The population of long-period transiting exoplanets \vspace{-2\baselineskip}

### 2016-09-19 document/ms.tex
damn
adding referee report and starting to respond

@@

\title{%
\vspace{\baselineskip}
The population of long-period transiting exoplanets
\vspace{-2.5\baselineskip}  % OMG AASTEX6 IS SO BROKEN
}

@@

This detection efficiency must then be combined with the geometric transit
probability function and the window function.
For the star $k$, the geometric transit probability is given by
\citep{Winn:2010}
\begin{eqnarray}
Q_{\mathrm{geom},k} (\params) &=& \frac{R_{\star,k} + R}{a_k}
    \, \frac{1 + e\,\sin\omega}{1-e^2} \\
&=& \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}
    \, \left[\frac{1 + e\,\sin \omega}{1-e^2}\right]\,(R_{\star,k}+R)
    \, P^{-2/3}
\end{eqnarray}
where $R$ is the planet radius, $P$ is the orbital period, $e$ is the orbital
eccentricity, $\omega$ is the argument of periastron, $R_{\star,k}$ is
the radius of star $k$, and $M_{\star,k}$ is the star's mass.
All of these parameters are included in \params.

@@

We list the probabilities for each of our candidates to belong to each
hypothesis in Table~\ref{tab:catalog}.  We find that the two deepest signals in our
candidate catalog (9306307 and  10602068) are very likely to be EBs, though we
note that this result may be dominated by the fact that our planet population
is fixed to have a maximum radius of 1\,$R_{\rm J}$.  Most of the rest of the
candidates  have false positive probabilities below 10\%.  We do note that as
discussed in \sect{catalog}, 4754460 (for which we calculate a 5\% false positive
probability) does show a partial deep eclipse right at the end of the \kepler\
data that indicates that it is most likely an EB.  Apart from this, the expected
number of false positives among the candidates with $R < R_{\rm J}$, according
to these calculations, is about one.

>>>>

% Response
\newcommand{\response}[1]{{\color{blue}#1}}

@@

\title{%
\vspace{\baselineskip}
The population of long-period transiting exoplanets
\vspace{-2\baselineskip}  % OMG AASTEX6 IS SO BROKEN
}

@@

This detection efficiency must then be combined with the geometric transit
probability function and the window function.
For the star $k$, the geometric transit probability is given by
\citep{Winn:2010}
\begin{eqnarray}\eqlabel{geom-comp}
Q_{\mathrm{geom},k} (\params) &=& \frac{R_{\star,k} + R}{a_k}
    \, \frac{1 + e\,\sin\omega}{1-e^2} \\
&=& \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}
    \, \left[\frac{1 + e\,\sin \omega}{1-e^2}\right]\,(R_{\star,k}+R)
    \, P^{-2/3}
\end{eqnarray}
where $R$ is the planet radius, $P$ is the orbital period, $e$ is the orbital
eccentricity, $\omega$ is the argument of periastron, $R_{\star,k}$ is
the radius of star $k$, and $M_{\star,k}$ is the star's mass.
All of these parameters are included in \params.

\response{%
In \eq{geom-comp}, the term $(R_{\star,k}+R)$ takes grazing transits into
account.
This might seem counter intuitive because, as part of the search procedure, we
rejected candidates where the maximum likelihood model had a grazing transit.
However, since the measurement of $Q_{\mathrm{det},k}$ included a cut on the
measured impact parameter, we argue that the $Q_{\mathrm{det},k}$ already
takes this effect into account.
In other words, $Q_{\mathrm{det},k}$ quantifies the probability that a transit
of a given shape will be detected \emph{given that it transits at all} and
$Q_{\mathrm{geom},k}$~--~the way it is written in \eq{geom-comp}~--~is the
marginalized probability that the system will transit given its physical
parameters.
}

@@

\response{We list the probability that each candidate is a planet in
Table~\ref{tab:catalog}.} We find that the two deepest signals in our
candidate catalog (9306307 and  10602068) are very likely to be EBs, though we
note that this result may be dominated by the fact that our planet population
is fixed to have a maximum radius of 1\,$R_{\rm J}$.  Most of the rest of the
candidates  have false positive probabilities below 10\%.  We do note that as
discussed in \sect{catalog}, 4754460 (for which we calculate a 5\% false positive
probability) does show a partial deep eclipse right at the end of the \kepler\
data that indicates that it is most likely an EB.  Apart from this, the expected
number of false positives among the candidates with $R < R_{\rm J}$, according
to these calculations, is about one.
